% explain " but why did you do it"
\begin{siderules}
  \cvsection{Professional Experience}
  \begin{cventries}
    \cventry
    {C\#, JavaScript, jQuery, AWS, NodeJS, ASP.NET}
    {Miovision\hspace{0.15em} \bodyfontlight\itshape{- Full Stack Software Developer}}
    {Sept. 2020 - Dec. 2020}
    {Waterloo, Ontario}
    {
      \begin{cvitems}
        \item{Designed and implemented a customer support tool using \textbf{C\#} and \textbf{ASP.NET}, performing \textbf{mySQL} operations and improving support resolve times by \textbf{40\%} }
        \item{Developed an analytics library using \textbf{jQuery} and Segment API, analyzing user behavior for product improvements by capturing \textbf{20} unique events across \textbf{500+} daily users}
        % \item {Designed and developed loosely-coupled analytics framework using \textbf{jQuery} and Segment API, capturing  unique events across  daily users; data used analyze user behaviour for product improvement }
        % \item {Analytics solution is loosely-coupled, isolated, and reusable; allowing it to be implemented into 3 other company products}
        % \item {Architected and applied new pattern to configure and add analytic attributes throughout project. Pattern is inatrusive to the codebßase by leveraging the DOM hierarchy and event handlers}
        % The loosely-coupled and flexible nature of the designed allowed for use in several different applications with minimal additional work, increasing adoption and decreasing development time.
        % \item {Refactored over \textbf{20} controllers and scripts to improve maintainability; applied the \textbf{SOLID} principles and proper \textbf{OOP} design}
        \item {Create a microservice using \textbf{React} and \textbf{NodeJS} to upload and store study videos into \textbf{AWS S3}, increasing upload file size from 5GB to \textbf{5TB} and improving upload performance }
      \end{cvitems}
    }
    \cventry
    {C\#, AWS, ASP.NET, SQL, Terraform, NUnit}
    {Miovision\hspace{0.15em} \bodyfontlight\itshape{- Software Developer}}
    {Jan. 2020 - Apr. 2020}
    {Waterloo, Ontario}
    {
      \begin{cvitems}
        \item {Eliminated legacy application’s security vulnerabilities by implementing \textbf{AWS IAM} roles and \textbf{AWS Parameter}, automating role $\>$ $\>$ $\>$ $\>$ assignments and EC2 instantiation using \textbf{Terraform}}
        \item {Developed a new event-driven monitoring service to track user activity using \textbf{AWS Lambda (NodeJS)} and \textbf{EventBridge}, sending metrics to \textbf{Datadog}}
        % \item {Implemented new factory pattern method for AWS SDK in a legacy application (\textbf{ASP.NET}), that significantly improved scalability }
        % \item {Refactored the controller layer of a legacy product in \textbf{ASP.NET}, applying the \textbf{SOLID} principles and proper \textbf{OOP} design, thereby creating maintainable and testable code}
        \item {Created automated unit tests with NUnit framework, increasing test coverage by \textbf{50\%} and ensuring functionality is preserved}
      \end{cvitems}
    }
    \cventry
      {Python, VB.NET, OpenCV, SQL}
      {Lumentum\hspace{0.15em} \bodyfontlight\itshape{- Software Developer}}
      {May 2019 - Aug. 2019}
      {Ottawa, Ontario}
      {
        \begin{cvitems}
          \item {Developed a computer vision script (\textbf{OpenCV}) using \textbf{Python} to analyze tube sealing quality, eliminating manual validation of \textbf{500+ images} per day}
          \item {Built an automation application in \textbf{VB.NET} to aid in the manufacturing of optical devices, reducing cycle times by \textbf{15 minutes}}
          \item {Created a database migration shell script to ensure data consistency between QA and staging environments, removing the need to manually run stored procedures}
        \end{cvitems}
      }
    \cventry
      {C++, Python, OpenCV, VBA}
      {KingTiger Technology Inc.\hspace{0.15em} \bodyfontlight\itshape{- Junior Engineering}}
      {Aug. 2018 - Dec. 2018}
      {Toronto, Ontario}
      {
        \begin{cvitems}
          \item {Automated R.A.M inspection process by detecting module's orientation using \textbf{OpenCV (C++)}, saving \textbf{10+ minutes} of manual sorting}
          \item {Programmed a barcode scanner application using \textbf{Python}, \textbf{Z-Bar}, and \textbf{dlib}, allowing users to upload over \textbf{150} company assets }
        \end{cvitems}
      }
    % \cventry
    %   {VBA, SolidWorks}
    %   {Amphenol Canada \hspace{0.15em} \bodyfontlight\itshape{Engineering Assistant}}
    %   {May 2017 - Dec 2017}
    %   {Toronto, Ontario}
    %   {
    %     \begin{cvitems}
    %       \item {Streamlined sales order processes and accounts payable workflows by developing \textbf{VBA scripts} to pull and push sales quotation data between Excel files and forms}
    %     \end{cvitems}
    %   }
  \end{cventries}
\end{siderules}
